### 2018-04-28 doc/paper.tex
Adding beginning of description of K-fold algorithm.

@@

\subsection{\texorpdfstring{\(K\)}{K} Error Filtering}

\begin{center}
\begin{tikzpicture}[node distance = 0.2\textwidth]
    \node [box] (bj) {\(b_j\)};
    \node [box, below of=bj] (bn0) {\(b_j^{(n)}\)};
    \node [box, right of=bn0] (dbn0) {\(\partial b_j^{(n)}\)};
    \node [box, right of=dbn0] (ddbn0) {\(\partial^2 b_j^{(n)}\)};
    \node [box, right of=ddbn0] (dddbn0) {\(\partial^3 b_j^{(n)}\)};
    %%
    \node [box, below of=bn0] (bn1) {\(b_j^{(n - 1)}\)};
    \node [box, below of=dbn0] (dbn1) {\(\partial b_j^{(n - 1)}\)};
    \node [box, below of=ddbn0] (ddbn1) {\(\partial^2 b_j^{(n - 1)}\)};
    \node [box, below of=dddbn0] (dddbn1) {\(\partial^3 b_j^{(n - 1)}\)};
    %%
    \node [box, below of=bn1] (bn2) {\(b_j^{(n - 2)}\)};
    \node [box, below of=dbn1] (dbn2) {\(\partial b_j^{(n - 2)}\)};
    \node [box, below of=ddbn1] (ddbn2) {\(\partial^2 b_j^{(n - 2)}\)};
    \node [box, below of=dddbn1] (dddbn2) {\(\partial^3 b_j^{(n - 2)}\)};
    %%
    \path [line] (bn0) -- node[above] {\(w_1^{(n)}\)} (dbn0);
    \path [line] (dbn0) -- node[above] {\(w_2^{(n)}\)} (ddbn0);
    \path [line] (ddbn0) -- node[above] {\(w_3^{(n)}\)} (dddbn0);
    \node [empty-box, right of=dddbn0] (right0) {\(\cdots\)};
    \path [line] (dddbn0) -- node[above] {\(w_4^{(n)}\)} (right0);
    %%
    \path [line] (bn1) -- node[above] {\(w_1^{(n - 1)}\)} (dbn1);
    \path [line] (dbn1) -- node[above] {\(w_2^{(n - 1)}\)} (ddbn1);
    \path [line] (ddbn1) -- node[above] {\(w_3^{(n - 1)}\)} (dddbn1);
    \node [empty-box, right of=dddbn1] (right1) {\(\cdots\)};
    \path [line] (dddbn1) -- node[above] {\(w_4^{(n - 1)}\)} (right1);
    %%
    \path [line] (bn2) -- node[above] {\(w_1^{(n - 2)}\)} (dbn2);
    \path [line] (dbn2) -- node[above] {\(w_2^{(n - 2)}\)} (ddbn2);
    \path [line] (ddbn2) -- node[above] {\(w_3^{(n - 2)}\)} (dddbn2);
    \node [empty-box, right of=dddbn2] (right2) {\(\cdots\)};
    \path [line] (dddbn2) -- node[above] {\(w_4^{(n - 2)}\)} (right2);
    %%
    \path [line] (bj) -- (bn0);
    \path [line] (bn0) -- node[fill=white] {\(U_n(s)\)} (bn1);
    \path [line] (bn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (bn2);
    \node [empty-box-vert, below of=bn2] (bottom0) {\(\vdots\)};
    \path [line] (bn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom0);
    %%
    \path [line] (dbn0) -- node[fill=white] {\(U_n(s)\)} (dbn1);
    \path [line] (dbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dbn2);
    \node [empty-box-vert, below of=dbn2] (bottom1) {\(\vdots\)};
    \path [line] (dbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom1);
    %%
    \path [line] (ddbn0) -- node[fill=white] {\(U_n(s)\)} (ddbn1);
    \path [line] (ddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (ddbn2);
    \node [empty-box-vert, below of=ddbn2] (bottom2) {\(\vdots\)};
    \path [line] (ddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom2);
    %%
    \path [line] (dddbn0) -- node[fill=white] {\(U_n(s)\)} (dddbn1);
    \path [line] (dddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dddbn2);
    \node [empty-box-vert, below of=dddbn2] (bottom3) {\(\vdots\)};
    \path [line] (dddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom3);
\end{tikzpicture}
\end{center}

>>>>

In order to raise from twice the working precision to \(K\) times the
working precision, we continue using EFTs when computing
\(\widehat{\partial b}^{(k)}\). By tracking the round-off from each
floating point evaluation via an EFT, we can form a cascade of global errors:
\begin{align}
  b_j^{(k)} &= \widehat{b}_j^{(k)} + \partial b_j^{(k)} \\
  \partial b_j^{(k)} &= \widehat{\partial b}_j^{(k)} + \partial^2 b_j^{(k)} \\
  \partial^2 b_j^{(k)} &= \widehat{\partial^2 b}_j^{(k)} +
  \partial^3 b_j^{(k)} \\
  & \vdots \nonumber
\end{align}
In the same way local error can be tracked when updating
\(\widehat{b}_j^{(k)}\), it can be tracked for updates that happen down
the cascade:
\begin{alignat}{4}
  (1 - s) \cdot \widehat{b}_j^{(k + 1)} &+
  s \cdot \widehat{b}_{j + 1}^{(k + 1)} &&  &&=
  \widehat{b}_j^{(k)} &&+ \ell_{1, j}^{(k)} \\
  (1 - s) \cdot \widehat{\partial b}_j^{(k + 1)} &+
  s \cdot \widehat{\partial b}_{j + 1}^{(k + 1)} &&+ \ell_{1, j}^{(k)} &&=
  \widehat{\partial b}_j^{(k)} &&+ \ell_{2, j}^{(k)} \\
  (1 - s) \cdot \widehat{\partial^2 b}_j^{(k + 1)} &+
  s \cdot \widehat{\partial^2 b}_{j + 1}^{(k + 1)} &&+ \ell_{2, j}^{(k)} &&=
  \widehat{\partial^2 b}_j^{(k)} &&+ \ell_{3, j}^{(k)} \\
  &  &&  &&\vdots && \nonumber
\end{alignat}

In \texttt{CompDeCasteljau}, after a single stage of error filtering we
``give up'' and use \(\widehat{\partial b}^{(k)}\) instead of
\(\partial b^{(k)}\) (and don't keep around any information about the
round-off error). In order to obtain results that are as accurate as if
computed in \(K\) times the working precision, we must continue filtering
errors down \((K - 1)\) times, so that at the final level we compute
\(\widehat{\partial^{K - 1} b}^{(k)}\) and don't worry about round-off
error.

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
    \node [box] (bj) {\(b\)};
    \node [box, below of=bj] (bn0) {\(\widehat{b}^{(n)}\)};
    \node [box, right of=bn0] (dbn0) {\(\widehat{\partial b}^{(n)}\)};
    \node [box, right of=dbn0] (ddbn0) {\(\widehat{\partial^2 b}^{(n)}\)};
    \node [box, right of=ddbn0] (dddbn0) {\(\widehat{\partial^3 b}^{(n)}\)};
    %%
    \node [box, below of=bn0] (bn1) {\(\widehat{b}^{(n - 1)}\)};
    \node [box, below of=dbn0] (dbn1) {\(\widehat{\partial b}^{(n - 1)}\)};
    \node [box, below of=ddbn0] (ddbn1) {\(\widehat{\partial^2 b}^{(n - 1)}\)};
    \node [box, below of=dddbn0] (dddbn1) {\(\widehat{\partial^3 b}^{(n - 1)}\)};
    %%
    \node [box, below of=bn1] (bn2) {\(\widehat{b}^{(n - 2)}\)};
    \node [box, below of=dbn1] (dbn2) {\(\widehat{\partial b}^{(n - 2)}\)};
    \node [box, below of=ddbn1] (ddbn2) {\(\widehat{\partial^2 b}^{(n - 2)}\)};
    \node [box, below of=dddbn1] (dddbn2) {\(\widehat{\partial^3 b}^{(n - 2)}\)};
    %%
    \path [line] (bn0) -- node[above] {\(\widehat{\ell}_1^{(n)}\)} (dbn0);
    \path [line] (dbn0) -- node[above] {\(\widehat{\ell}_2^{(n)}\)} (ddbn0);
    \path [line] (ddbn0) -- node[above] {\(\widehat{\ell}_3^{(n)}\)} (dddbn0);
    \node [empty-box, right of=dddbn0] (right0) {\(\cdots\)};
    \path [line] (dddbn0) -- node[above] {\(\widehat{\ell}_4^{(n)}\)} (right0);
    %%
    \path [line] (bn1) -- node[above] {\(\widehat{\ell}_1^{(n - 1)}\)} (dbn1);
    \path [line] (dbn1) -- node[above] {\(\widehat{\ell}_2^{(n - 1)}\)} (ddbn1);
    \path [line] (ddbn1) -- node[above] {\(\widehat{\ell}_3^{(n - 1)}\)} (dddbn1);
    \node [empty-box, right of=dddbn1] (right1) {\(\cdots\)};
    \path [line] (dddbn1) -- node[above] {\(\widehat{\ell}_4^{(n - 1)}\)} (right1);
    %%
    \path [line] (bn2) -- node[above] {\(\widehat{\ell}_1^{(n - 2)}\)} (dbn2);
    \path [line] (dbn2) -- node[above] {\(\widehat{\ell}_2^{(n - 2)}\)} (ddbn2);
    \path [line] (ddbn2) -- node[above] {\(\widehat{\ell}_3^{(n - 2)}\)} (dddbn2);
    \node [empty-box, right of=dddbn2] (right2) {\(\cdots\)};
    \path [line] (dddbn2) -- node[above] {\(\widehat{\ell}_4^{(n - 2)}\)} (right2);
    %%
    \path [line] (bj) -- (bn0);
    \path [line] (bn0) -- node[fill=white] {\(U_n(s)\)} (bn1);
    \path [line] (bn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (bn2);
    \node [empty-box-vert, below of=bn2] (bottom0) {\(\vdots\)};
    \path [line] (bn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom0);
    %%
    \path [line] (dbn0) -- node[fill=white] {\(U_n(s)\)} (dbn1);
    \path [line] (dbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dbn2);
    \node [empty-box-vert, below of=dbn2] (bottom1) {\(\vdots\)};
    \path [line] (dbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom1);
    %%
    \path [line] (ddbn0) -- node[fill=white] {\(U_n(s)\)} (ddbn1);
    \path [line] (ddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (ddbn2);
    \node [empty-box-vert, below of=ddbn2] (bottom2) {\(\vdots\)};
    \path [line] (ddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom2);
    %%
    \path [line] (dddbn0) -- node[fill=white] {\(U_n(s)\)} (dddbn1);
    \path [line] (dddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dddbn2);
    \node [empty-box-vert, below of=dddbn2] (bottom3) {\(\vdots\)};
    \path [line] (dddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom3);
\end{tikzpicture}
\caption{Filtering errors}
\end{figure}

@@
